Network Cascades

### 2016-09-23 paper/paper.tex
Add some more related work

An introduction to generating functions can be found in \cite{wilf1994generatingfunctionology}. Tthis version of the book is referenced by Watts et. al. in his paper below.

@@

\section{Conclusion}\label{sec:summary}

>>>>

An introduction to generating functions can be found in \cite{wilf1994generatingfunctionology}. This version of the book is referenced by Watts et. al. in his paper below.

@@

There also exists an extension to Watt's model for use with temporal networks in \cite{temporal}. Those networks add the dimension of time, which means, for instance, links between nodes may only exist at certain points in time. This is clearly a useful property for extending Watt's model, where nodes periodically check the state of their neighbors, since it can be modelled in more detail using a temporal network. The paper contrasts their approaches with Watt's original model and also tries out a version where thresholds are absolute numbers, rather than relative fractions of neighbors.

\newpage
\section{Conclusion}\label{sec:summary}
